Milestone 2: Model Validation

### 2019-11-06 perf_release_criteria/milestone_3/ms_2_validation.Rmd
Adding in text.

# filter out categorical
features_top10 <- df_train_f %>% 
  select(features_top10) %>% 
  # select_if(is.numeric) %>% 
  names()
features_top10_eq <- df_train_f %>% 
  select(features_top10_eq) %>% 
  # select_if(is.numeric) %>% 
  names()
```

@@

covs <- df_train_f %>%
  select(-perf_metrics) %>%
  select(-content_crashes) %>%
  select(-client_id) %>%
  select(-label) %>%
  select(-is_release) %>%
  select(-app_version) %>%
  # select_if(is.numeric) %>% # Mahalanobis constraint
  names()

@@

@@

@@

Hyperparameters:

* Determined in `hyperparameter_tuning_nn_malahanobis.Rmd`
*

```{r nn_mal}
nn.mal <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, distance = "mahalanobis")
```

@@

* The bootsraps and training datasets!

>>>>

# filter out categorical
features_top10 <- df_train_f %>% 
  select(features_top10) %>% 
  select_if(is.numeric) %>% 
  names()
features_top10_eq <- df_train_f %>% 
  select(features_top10_eq) %>% 
  select_if(is.numeric) %>% 
  names()
```

@@

covs <- df_train_f %>%
  select(-perf_metrics) %>%
  select(-content_crashes) %>%
  select(-client_id) %>%
  select(-label) %>%
  select(-is_release) %>%
  select(-app_version) %>%
  select_if(is.numeric) %>% # Mahalanobis constraint
  names()

@@

```{r scorer}
score_model <- function(bts, df_match, df_val, workers){
  if (missing(workers)) workers = detectCores()
  cl <- makePSOCKcluster(workers) 
  registerDoParallel(cl)
  final <- tryCatch({
    scores <- foreach(i=1:length(bts), 
                      .packages = c('dplyr', 'transport'), 
                      .export=c('calc_score', 'calc_cms', 'get_m2_metric_map')) %dopar% {
                        bt <- bts[[i]]
                        test <- df_val %>% 
                          right_join(data.frame(client_id = bt, stringsAsFactors=FALSE), by='client_id', 'right')

                        df_scores <- test %>%
                          bind_rows(df_match)

                        score <- calc_score(df_scores, get_m2_metric_map())
                        score
                        }
    scores <- unlist(scores)
    c(mean = mean(scores), median = median(scores))
  }, 
  error = function(cond){
    message(paste("Bootstrap validation failed: ", cond))
    return(NA)
  },
  finally = {
    stopCluster(cl)
  }
  )
  return(final)
}
```

@@

Two matching methods were ultimately tested, as CEM and subclassing were producing extremely poor results.

* nearest-neighbors
* genetic matching

Feature selection and hyperparameter tuning for the nearest-neighbors models were all trained using the `MatchIt` library.  The following method trains these models using the full training dataset.

@@

Hyperparameters: `hyperparameter_tuning_nn_malahanobis.Rmd`

* `caliper` = 0.25
* `calcloset` = TRUE
* `ratio` = 2
* `replace` = FALSE

```{r nn_mal_fs1}
nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
score_model(bts, nn.mal.fs1$matched, df_rel_val)
```

```{r nn_mal_fs3}
nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
                        caliper = 0.25, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
score_model(bts, nn.mal.fs3$matched, df_rel_val)
```

```{r nn_mal_fs5}
nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
                        caliper = 0.25, calclosest = TRUE, ratio = 1, 
                        distance = "mahalanobis")
score_model(bts, nn.mal.fs3$matched, df_rel_val)
```

## GAM

# TODO

* Build validation methods
    - Plots
    - Scoring
    - Everything I would use for dashboard

@@

* The bootstraps and training datasets!

```{r}
save(nn.mal, 
     file = '')
```
